%-----------------------------------------------------------------------------------------------------------------
\prefacesection{Acknowledges}
%-----------------------------------------------------------------------------------------------------------------
I would like to thank my supervisors José Boaventura Ribeiro da Cunha, António Paulo Gomes Mendes Moreira and Luís Freitas Rocha for believing in my capacity and gave opportunities to develop this work. The assistance and the transmitted knowledge were unrivalled. 


Thanks to the University of Trás-os-Montes and Alto Douro and INESC TEC that provided all the conditions to carry out this work. The CRIIS' group and facilities are incredible.

As a foreign student, I never expected to achieve this abroad academic path but I would like o express my special thanks to professor António Paulo Gomes Mendes Moreira. You discovered me and gave me the chance to trail this professional way.

It was not easy, besides the inherent PhD complexity I faced difficulties by staying away from family,  for the surgeries I had and getting through the pandemic period. However, an important lesson was taken: never desist, insist, focus and persevere. Thus, father - João Carlos de Souza - and mother - Celimar Alves Carvalho -, this was what you educated me and thank you so much for all effort that you faced with your son far away. Many thanks to all my distant family.

Thanks to all my friends, from Brazil to Portugal, and to my girlfriend who are present and gave me support and happiness during this challenging period. 

To all my laboratory colleagues, thank you for the laughs at lunchtime and for the advice and technical/theoretical support. Specially thanks to Carlos Costa who provided discussions and criticism which improve and propitiated new ideas formulation. Professors Manuel Silva and Hélio Sousa, thank you for the advice and for believing in my competence. 

It's worthwhile to mention my gratitude to the FCT which accepted my thesis plan proposal and promote its development.


\EspacoMedio
\EspacoMedio
\EspacoMedio
\noindent UTAD, \hfill João Pedro Carvalho de Souza \\ Vila Real, xx de xxxxx de 20XX
%-----------------------------------------------------------------------------------------------------------------
