%\prefacesection{R\&D Companion Projects and Industrial Deployment}
\prefacesection{Projects Deployment}

The following R\&D projects deployed this Ph.D. thesis proposal:

\begin{comment} %%%%%%%%%%%%%%%%%%
\begin{itemize_jp}
    \item \textbf{Fasten:} Flexible  and  Autonomous  Manufacturing  Systems  for  Custom-Designed Products. \url{http://www.fastenmanufacturing.eu/}. European Union’s Horizon 2020 research and innovation programme under grant agreement 777096.
    \item \textbf{Mari4 Yard:} Leverages the potential of Internet of Things (IoT), mobile and ubiquitous ICT tools, and robotics to develop user-centric solutions for flexible and modular manufactoring and thus implement a novel connectes shipyard. \url{https://www.mari4yard.eu/}. European Union’s Horizon 2020 research and innovation programme under Grant Agreement 101006798.
    \item \textbf{Produtech 4S\&C:} \url{http://mobilizadores.produtech.org/en/produtech-4-s-c?set_language=en}
    
    \item \textbf{Produtech SIF:} \url{http://mobilizadores.produtech.org/en/produtech-sif}
\end{itemize_jp}
\end{comment} %%%%%%%%%%%%%%%%%%



\begin{itemize_jp}
    \item \textbf{Fasten.} European Union’s Horizon 2020 research and innovation programme under grant agreement 777096. \url{http://www.fastenmanufacturing.eu/}.
    \item \textbf{Mari4 Yard.}  European Union’s Horizon 2020 research and innovation programme under Grant Agreement 101006798. \url{https://www.mari4yard.eu/}.
    \item \textbf{Produtech 4S\&C.}   European Regional Development Fund, through the Operational Programme for Competitiveness and Internationalisation - COMPETE 2020 Programme under the Portugal 2020 Partnership Agreement with reference POCI-01-0247-FEDER-046102. \url{http://mobilizadores.produtech.org/en/produtech-4-s-c}
    
    \item \textbf{Produtech SIF.} European Regional Development Fund, through the Operational Programme for Competitiveness and Internationalisation - COMPETE 2020 Programme under the Portugal 2020 Partnership Agreement with reference POCI-01-0247-FEDER-024541. \url{http://mobilizadores.produtech.org/en/produtech-sif}
\end{itemize_jp}


